\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2015-04-20 paper/subdocuments/results.Rnw
update latest version of paper updated sissGini Data with HBS data several updates of results.Rnw

#bern kantonal (liegt lokal wegen datenschutz)
#try(bern_kt <- read.dta("H:/Assessing Inequalty/taxDataBE2012.dta"))
try(bern_kt<-read.csv("U:/Persönlich/Forschung/Uni Bern/BFH-Grunddaten 2012 Output V1.1.csv",sep=";"))
try(bern_kt <- read.csv("G:/stick/bern//BFH-Grunddaten 2012 Output V1.1.csv",sep=";"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige
bern_kt <- filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31")
names(bern_kt)<-tolower(names(bern_kt))
set0 <- function(x) ifelse(x<0 | is.na(x),0,x)
bern_kt <- bern_kt %>% mutate(primeink2 = set0(hem)+set0(nem)+set0(esm)+set0(sgm)+set0(hef)+set0(nef)+set0(esf)+set0(sgf)+set0(erfolg_s)+set0(erfolg_l)+set0(kk_ertrag)+set0(bg_ertrag)+ set0(wsert)+set0(eink_lieg)+set0(eg_ertrag)+set0(stm)+set0(stf)+set0(lov)+set0(lmv)+set0(lng))

@@

<<bern_kantonale_analysen>>=
# core variables from bern 2002-2012
bern <- read.dta("G:/stick/bern/mini_taxdata_BE_all.dta")
bern_gini <- bern %>%
  mutate(stbeink_no_dbs = stbeink_BUND - eink_st_dbs,
         stbeink_no_tax = stbeink_BUND - steuern_eink) %>% # nur steuern auf einkommen (nicht vermögen) werden abgezogen
  group_by(stj) %>%
  summarise(G_TOTEINK = gini(TOTEINK),
            G_stbeink_BUND = gini(stbeink_BUND),
            G_stbeink_no_dbs = gini(stbeink_no_dbs),
            G_stbeink_no_tax = gini(stbeink_no_tax))

@@

# legend order
levels(bern_gini_long$Income) <- c("total income", "taxable income", "taxable income after federal income tax", "taxable income after all income taxes")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("taxable income", "taxable income after federal income tax", "taxable income after all income taxes","total income"))

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  #scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=pointsize)+
  geom_line(aes(linetype=Income),size=linesize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Gini coefficients of different income measures")
fig_bern_gini

@@

### Fetch Ginis from different survey data
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini<-read.csv("../../data/swissGini.csv",header=TRUE,sep=";")

@@

### and for the rest of Ginis:
estv <- read.dta("../../data/steuerdaten20141126_stata12.dta")

@@

all_gini_long$Data <- factor(all_gini_long$Data,levels=c("FTA","LIS","EU.SILC","HBS"))
benplot <- ggplot(data=na.omit(all_gini_long),
  aes(y=Gini,x=Year,shape=Data,linetype=Data))+
  ylab("Gini from different sources") +
  scale_y_continuous(limits=c(0.18,0.45)) +
  scale_x_continuous(limits=c(1945,2012),breaks=number_ticks(10)) +
  geom_point(size=pointsize)+
  geom_line(size=linesize)+
  #geom_text(aes(label=annotation,y=ypos),color="#555555",size=3)+
  #geom_segment(aes(x = 1921, y = 0.27, xend = 1921, yend = Gini[Year==1921]),color="#aaaaaa") +
  #geom_segment(aes(x = 1940, y = 0.305, xend = 1940, yend = Gini[Year==1940]),color="#aaaaaa") +
  #geom_segment(aes(x = 1945.5, y = 0.29, xend = 1945.5, yend = Gini[Year==1945.5]),color="#aaaaaa") +
  #geom_segment(aes(x = 1967.5, y = 0.285, xend = 1967.5, yend = Gini[Year==1967.5]),color="#aaaaaa") +
  theme_bw()+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))

>>>>

#bern kantonal (liegt lokal wegen datenschutz)
try(bern_kt<-read.dta("U:/Persönlich/Forschung/Uni Bern/taxdata_BE_12.dta"))
try(bern_kt <- read.csv("G:/stick/bern//BFH-Grunddaten 2012 Output V1.1.csv",sep=";"))
#> nrow(bern_kt)
#[1] 622368
nrow(filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31"))
#[1] 605975 wir filtern ca. 3% unterjährige
bern_kt <- filter(bern_kt,VON=="2012-01-01",BIS=="2012-12-31")
bern_kt <- filter(bern_kt,Satzeink_BUND<=TOTEINK,erm==0)
bern_kt <- filter(bern_kt,erm==0)
names(bern_kt)<-tolower(names(bern_kt))
set0 <- function(x) ifelse(x<0 | is.na(x),0,x)
bern_kt <- bern_kt %>% mutate(primeink2 = set0(hem)+set0(nem)+set0(esm)+set0(sgm)+set0(hef)+set0(nef)+set0(esf)+set0(sgf)+set0(erfolg_s)+set0(erfolg_l)+set0(kk_ertrag)+set0(bg_ertrag)+ set0(wsert)+set0(eink_lieg)+set0(eg_ertrag)+set0(stm)+set0(stf)+set0(lov)+set0(lmv)+set0(lng))

@@

<<bern_kantonale_analysen>>=
# core variables from bern 2002-2012
try(bern <- read.dta("G:/stick/bern/mini_taxdata_BE_all.dta"))
try(bern<-read.dta("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/Kantonale Steuerdaten/Bern/taxdata_BE_reduced.dta"))
P:\WGS\FBS\ISS\Projekte laufend\SNF Ungleichheit\Datengrundlagen\Kantonale Steuerdaten\Bern
bern <- filter(bern_kt,Satzeink_BUND<=TOTEINK,erm==0)
bern <- filter(bern_kt,erm==0)
bern$verfeink<-bern$TOTEINK+bern$privattrans_bez-bern$steuertotal

#bern_gini <- bern %>%
#  mutate(stbeink_no_dbs = stbeink_BUND - eink_st_dbs,
#         stbeink_no_tax = stbeink_BUND - steuern_eink) %>% # nur steuern auf einkommen (nicht vermögen) werden abgezogen
#  group_by(stj) %>%
#  summarise(G_TOTEINK = gini(TOTEINK),
#            G_stbeink_BUND = gini(stbeink_BUND),
#            G_stbeink_no_dbs = gini(stbeink_no_dbs),
#            G_stbeink_no_tax = gini(stbeink_no_tax))

bern_gini <- bern %>%
  group_by(stj) %>%
    summarise(G_TOTEINK = gini(TOTEINK),
            G_satzeink_BUND = gini(Satzeink_KANTON),
            G_TOTEINK = gini(TOTEINK),
            G_verfeink = gini(verfeink))

@@

# legend order
levels(bern_gini_long$Income) <- c("total income", "taxable income", "Disposable income")
bern_gini_long$Income <- factor(bern_gini_long$Income,levels=c("total income", "taxable income", "Disposable income")

fig_bern_gini <- ggplot(bern_gini_long, aes(x=stj,y=Gini)) +
  #scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(breaks=number_ticks(5)) +
  geom_point(aes(shape=Income),size=pointsize)+
  geom_line(aes(linetype=Income),size=linesize)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Gini coefficients of different income concepts")
fig_bern_gini

@@

### Fetch Ginis from different survey data
number_ticks <- function(n) {function(limits) pretty(limits, n)}
try(swissGini<-read.csv("../../data/swissGini.csv",header=TRUE,sep=";"))
try(swissGini<-read.csv("C:/Users/hlo1/swiss_inequality_development/data/swissGini.csv",header=TRUE,sep=";"))

@@

### and for the rest of Ginis:
try(estv <- read.dta("../../data/steuerdaten20141126_stata12.dta"))
try(estv <- read.dta("C:/Users/hlo1/swiss_inequality_development/data/steuerdaten20141126_stata12.dta"))

@@

all_gini_long$Data <- factor(all_gini_long$Data,levels=c("FTA","LIS","EU.SILC","HBS"))

benplot <- ggplot(data=na.omit(all_gini_long),
  aes(y=Gini,x=Year,shape=Data,linetype=Data))+
  ylab("Gini") +
  scale_y_continuous(limits=c(0.18,0.45)) +
  scale_x_continuous(limits=c(1945,2012),breaks=number_ticks(10)) +
  geom_point(size=4)+
  geom_line(size=1)+
  #geom_text(aes(label=annotation,y=ypos),color="#555555",size=3)+
  #geom_segment(aes(x = 1921, y = 0.27, xend = 1921, yend = Gini[Year==1921]),color="#aaaaaa") +
  #geom_segment(aes(x = 1940, y = 0.305, xend = 1940, yend = Gini[Year==1940]),color="#aaaaaa") +
  #geom_segment(aes(x = 1945.5, y = 0.29, xend = 1945.5, yend = Gini[Year==1945.5]),color="#aaaaaa") +
  #geom_segment(aes(x = 1967.5, y = 0.285, xend = 1967.5, yend = Gini[Year==1967.5]),color="#aaaaaa") +
  theme_bw()+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))
